Review questions list

### 2020-10-17 docs/paper/paper.tex
Fixed the replies for Reviewer 2 and 3

The GAN can be trained by diverse metrics \cite{goodfellow2014generative, lucic2018gans}]. In this work Wasserstein distance metric (WGAN) is employed \cite{arjovsky2017wasserstein}. In this system, discriminator is named as critic and it measures the distance between the generated and the real data. The distinguishing feature of the WGAN compared to other methods is the ability to determine a stopping criteria. In a regular GAN system, training is stopped when the generated data is deemed viable by an observer. GAN is frequently used in image, video or audio generation, where human is used effectively in the loop. In our case, it is not viable for a human to judge the generated data, therefore, automating this procedure to remove the human in-the-loop can lead to over or under-fitting, which may degrade the performance. On the other hand, WGAN uses an adaptive stopping criteria that can easily overcome the aforementioned disadvantages. Additionally, Gradient penalty is incorporated to improve the WGAN as described in \cite{gulrajani2017improved}. This proposed enhanced WGAN system converges in a stable manner without requiring further fine tuning the hyper-parameters of the system. % The flowchart of this proposed system is illustrated in Figure \ref{fig:gan}.

@@

where $\lambda$ is the operating wavelength, $n$ is the Refractive Index (RI), $B_{1,2,3}$ and  $C_{1,2,3}$ are the  Sellmeier constants~\cite{bjarklev2003PCF}.

@@

In the following subsections, we have performed experiments to show the performance of the base ANN system by its own comparing with the state-of-the-art method in the literature \cite{paper0}, improvement gained by employing GAN phase, and finally the computational advantages of using ANN over the simulator. 5000 training epochs are used for  \cite{paper0} as suggested in the original paper. All numeric comparison results are averaged over multiple executions: 9-fold testing for SPR dataset and 10-fold testing for \dszero. Non-averaged data used in figures, such as configuration estimation, are selected from non-extreme cases for the compared methods.
%
%\begin{table}
%	\centering
%	\caption{Datasets that are used in experiments}
%	\begin{tabular}{l|l|l}
%		~ & SPR & \dszero \\\hline
%		Samples & 432 & 1117\\
%		Configurations & 9 & - \\
%		Parameters & 7 & 5 \\
%		Output & $log_{loss}$ & $log_{loss}$ \\
%		Testing & 48 (1 configuration) & 10\% \\
%		Testing method & 9-fold & 10-fold \\
%	\end{tabular}
%	\label{tbl:dataset}
%\end{table}
%

@@

\begin{table}
	\caption{Detailed performance analysis in MSE}
	\centering
	\begin{tabular}{l|l|l|l|l|l|l}
		Dataset & \multicolumn{3}{c|}{SPR} & \multicolumn{3}{c}{\dszero{}} \\\hline
		Method & \multicolumn{2}{c|}{Proposed} & \cite{paper0}  & \multicolumn{2}{c|}{Proposed}   & \cite{paper0} \\\hline
		GAN Phase 			& Yes            & No    &  No     &   Yes            & No             & No    \\\hline
		Average   			& \textbf{0.314} & 0.894 & 0.987   &   \textbf{0.134} & 0.156          & 0.167 \\
		Best      			& \textbf{0.006} & 0.042 & 0.047   &   0.095          & \textbf{0.093} & 0.106 \\
		Worst     			& \textbf{1.102} & 6.792 & 5.955   &   \textbf{0.181} & 0.265          & 0.416 \\
		Std. dev.       	& \textbf{0.437} & 2.213 & 1.940   &   \textbf{0.031} & 0.046          & 0.090 \\
	\end{tabular}
	\label{tbl:all}
\end{table}

>>>>

The GAN can be trained by diverse metrics \cite{goodfellow2014generative, lucic2018gans}]. In this work Wasserstein distance metric (WGAN) is employed \cite{arjovsky2017wasserstein}. In this system, discriminator is named as critic and it measures the distance between the generated and the real data. The distinguishing feature of the WGAN compared to other methods is the ability to determine a stopping criteria. \hl{In a regular GAN system, training is stopped when the generated data is deemed viable by an observer. GAN is frequently used in image, video or audio generation, where human is used effectively in the loop. In our case, it is not viable for a human to judge the generated data, therefore, automating this procedure to remove the human in-the-loop can lead to over or under-fitting, which may degrade the performance. On the other hand, WGAN uses an adaptive stopping criteria that can easily overcome the aforementioned disadvantages.} Additionally, Gradient penalty is incorporated to improve the WGAN as described in \cite{gulrajani2017improved}. This proposed enhanced WGAN system converges in a stable manner without requiring further fine tuning the hyper-parameters of the system. % The flowchart of this proposed system is illustrated in Figure \ref{fig:gan}.

@@

where $\lambda$ is the operating wavelength, $n$ is the \hl{Refractive Index (RI)}, $B_{1,2,3}$ and  $C_{1,2,3}$ are the  Sellmeier constants~\cite{bjarklev2003PCF}.

@@

In the following subsections, we have performed experiments to show the performance of the base ANN system by its own comparing with the state-of-the-art method in the literature \cite{paper0}, improvement gained by employing GAN phase, and finally the computational advantages of using ANN over the simulator. 5000 training epochs are used for  \cite{paper0} as suggested in the original paper. All numeric comparison results are averaged over multiple executions: 9-fold testing for SPR dataset and 10-fold testing for \dszero. \hl{The number of testing samples used in SPR dataset experiments is 48, \dszero{} experiments is 112.} Non-averaged data used in figures, such as configuration estimation, are selected from non-extreme cases for the compared methods.
%
%\begin{table}
%	\centering
%	\caption{Datasets that are used in experiments}
%	\begin{tabular}{l|l|l}
%		~ & SPR & \dszero \\\hline
%		Samples & 432 & 1117\\
%		Configurations & 9 & - \\
%		Parameters & 7 & 5 \\
%		Output & $log_{loss}$ & $log_{loss}$ \\
%		Testing & 48 (1 configuration) & 10\% \\
%		Testing method & 9-fold & 10-fold \\
%	\end{tabular}
%	\label{tbl:dataset}
%\end{table}
%

@@

\begin{table}
	\caption{\hl{Detailed performance analysis in MSE}}
	\centering
	\begin{tabular}{l|l|l|l|l|l|l}
		Dataset & \multicolumn{3}{c|}{SPR} & \multicolumn{3}{c}{\dszero{}} \\\hline
		Method & \multicolumn{2}{c|}{Proposed} & \cite{paper0}  & \multicolumn{2}{c|}{Proposed}   & \cite{paper0} \\\hline
		GAN Phase 			& Yes            & No    &  No     &   Yes            & No             & No    \\\hline
		Average   			& \textbf{0.314} & 0.894 & 0.987   &   \textbf{0.134} & 0.156          & 0.167 \\
		Best      			& \textbf{0.006} & 0.042 & 0.047   &   0.095          & \textbf{0.093} & 0.106 \\
		Worst     			& \textbf{1.102} & 6.792 & 5.955   &   \textbf{0.181} & 0.265          & 0.416 \\
		Std. dev.       	& \textbf{0.437} & 2.213 & 1.940   &   \textbf{0.031} & 0.046          & 0.090 \\
	\end{tabular}
	\label{tbl:all}
\end{table}

### 2020-10-17 docs/revision/reply.tex
Fixed the replies for Reviewer 2 and 3

	We would like to thank the respected reviewer for their valuable comments that helped us to improve the quality of this article. We would also like to state that we were unable to add all the requested details directly to the paper due to the page limitation. However, in this reply, we have tried to address all points that are raised by the reviewers to the best of our ability. Also due to small changes in the manuscript, reference numbers have shifted. We have used the reference numbers as discussed by the reviewers and offered the new reference number at the end of each reply.

@@

	During our initial \hl{systematic experiments; instead of "studies"}, we have studied the effect of the network architecture on the accuracy. During these studies we have found 5 layers are necessary for ANN to be able estimate the loss curve. Specifically, in SPR dataset, this requirement is evident. Higher number of layers \hl{not only potentially leads to overfitting, but also to an  increase in} the required number of samples to train causing further problems. Similar situation exists for the number of neurons. However, it is possible that there might be a better combination of layers and neurons as we have not performed any exhaustive optimization on the neural network.

@@

	As the respected reviewer pointed out, we have used our SPR dataset in Figure 4c as well as Figure 4a which includes all configurations. The aim here is to show that the changes in the state-of-the-art is necessary to enable the ANN architecture to handle more complex systems. We should point out in here that this improved network is not the focus of our research, it is merely a prerequisite to the more important contribution of GAN phase, which in turn allows us to tackle the more difficult problem. In Figure 6, the comparison is drawn using the proposed architecture with and without GAN phases. The method in [18] is excluded in this graph as the improvement that can obtained by applying GAN phase to the network proposed in [18] does not yield any net benefit. In the text below we would like to explain our rationale for modifying the state-of-the-art to the proposed architecture.

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

>>>>

	We would like to thank the respected reviewers for their valuable comments that helped us to improve the quality of this article. We would also like to state that we were unable to add all the requested details directly to the paper due to the page limitation. However, in this reply, we have tried to address all points that are raised by the reviewers to the best of our ability. Also due to small changes in the manuscript, reference and figure numbers are shifted. We have used these numbers as discussed by the reviewers and offered the new numbers at the end of each reply.

@@

	During our initial experiments, we have studied the effect of the network architecture on the accuracy. During these studies we have found 5 layers are necessary for ANN to be able estimate the loss curve. Specifically, in SPR dataset, this requirement is evident. Higher number of layers increases both the risk of overfitting and the required number of samples to train the network, causing further problems. Similar situation exists for the number of neurons. However, it is possible that there might be a better combination of layers and neurons as we have not performed any exhaustive optimization on the neural network.

@@

	As the respected reviewer pointed out, we have used our SPR dataset in Figure 4c as well as Figure 4a which includes all configurations. The aim here is to show that the changes in the state-of-the-art is necessary to enable the ANN architecture to handle more complex systems. We should point out in here that this improved network is not the focus of our research, it is merely a prerequisite to the more important contribution of GAN phase, which in turn allows us to tackle this more difficult problem. In Figure 6, the comparison is drawn using the proposed architecture with and without GAN phases. The method in [18] is excluded in this graph as the improvement that can obtained by applying GAN phase to the network proposed in [18] does not yield any net benefit. In the text below we would like to explain our rationale for modifying the state-of-the-art to the proposed architecture.

@@

	We would like to thank the respected reviewer for his help in finding these problems. We have carefully reread the manuscript and corrected spelling and grammatical errors

@@

	Respected reviewer poses a very important remark. Our primary aim in this paper is to introduce data augmentation to this field as data augmentation has never used in this field before. This also means that there are no prior experiments to draw comparisons to. We have selected GAN as it is shown to be effective in many fields. We do believe the alternative generative methods may have similar results and should be explored. However, each of these methods should be explained, implemented and optimized for this problem. This will increase the scope of this study substantially and will require us to expand the paper further. Even though the former is possible; due to the page limit put forth by the journal, the latter is not.

@@

	We have used the networks described in [18] as a starting point and applied changes that are known to solve the issues that are surfaced when this method is applied to a more difficult dataset. While we cannot give an exact time frame to the solution, we have spent at least several weeks adapting the ANN for this difficult problem.

@@

	We would like to thank the reviewer for noticing the missing metric in the table, it is indeed MSE. We have updated the table title to include the metric.

@@

	We have added the definition of RI in the manuscript.

@@

	In original manuscript we have omitted the validation graph to save space. We have included the validation curve in the revised manuscript as Fig. 4.

@@

	The requested MSEs are provided on the graphs in the new manuscript. \\

@@

	We are thankful for the reviewer's valuable comment. This is the exact reason we have used WGAN. WGAN does not require human judgment, instead, it uses an adaptive stopping criteria. It might be possible to embed simulation approach into GAN training phase to offload judgment duty. This approach requires an extensive study of simulation systems and further experiments to test the viability of this approach. However, authors will consider respected reviewer's suggestion for a future study.

	WGAN features its own loss function to determine stopping criteria. During the experiments, we have observed that the loss curve of WGAN converges to zero during the training. In addition to this observation, to ensure the generated data is relevant, we have filtered out the generated samples that fall outside the bounding box of the actual samples.

@@

	We are sorry for not openly stating the requested information in the manuscript. We have expanded the information regarding the training and test samples in the fourth paragraph of the Experimental setup section. We include this information below for easy access:

	For the SPR set: we have used 9 fold testing, we used 336 samples for training, 48 for validation and 48 for testing. Please note that each geometric configuration has 16 data point per analyte making up to 48 for the 3 analytes used. In this experimental setup, each configuration set (48 samples) are tested separately in its own fold and the reported results are the average of these 9 folds.

	For the PCF set: we have used 10 fold testing, 112 samples are used for testing, 101 (10\% of training) samples are used for validation and the rest is used for training. For this 10 fold testing, we have randomly shuffled the samples into 10 bins, each bin is used for testing over these folds and reported results are the average of these 10 folds.

@@

	Data augmentation is not perfect, the augmented data contains some degree of error. When the number of samples are too low, such is the state in SPR dataset, the performance loss due to low number of samples massively out-weighs the error introduced by the augmented samples. However, as the number of generated samples increase, this error accumulates and starts to reduce the performance of the overall system. We would like to point out that while 1000 augmented samples achieve the best result, it requires 3000 or more augmented samples to perform worse than no augmentation. We have also added more data points to Fig 5 to answer this question with surety.

@@

	There are two reasons for the deviation in Fig 6a. The first and most important is the fact that SPR dataset experiments is much more difficult compared to PCF dataset experiments. The most important difference here is the testing strategy. In PCF dataset, the testing samples are selected randomly from all the samples in the dataset. However, in SPR dataset, testing samples are from a completely new geometric configuration, in other words, we never show the testing configuration to the ANN system and expect it to estimate its loss function. Additionally, SPR dataset contains far fewer samples. The second reason for the variation is the range of the experiments, SPR experiment output is constrained in a small region, accentuating the deviation. There is certainly more variation the SPR dataset, however, the difference is not as high as Fig 6 suggests.

	Finally, it is possible to verify the results from Fig 6c as these are two of the individual geometric configurations that the ANN systems estimated. Even though there still is a deviation from the ground truth, ANN trained with the help of augmented samples is good at estimating the location of the peak.
